\huge A Usability Evaluation of Tor Launcher

### 2016-11-24 pets2017-paper/pets2017-paper.tex
Make degrees-of-freedom "df" presentation uniform.
I actually don't know if this should be roman or italic. It was roman in
one place and italic in the other. I made it roman in both places.

%success rate and version
Our interface changes did {\it not} have a significant impact on completion rates (Pearson's Chi-squared; $\chi^2 = 2.808$, $df = 2$, $p = 0.094$). That is, the slight differences in completion rates between E1-NEW vs E1-OLD, E2-NEW vs E2-OLD and E3-NEW vs E3-OLD are likely due to random chance.

>>>>

%success rate and version
Our interface changes did {\it not} have a significant impact on completion rates (Pearson's Chi-squared; $\chi^2 = 2.808$, $\mbox{df} = 2$, $p = 0.094$). That is, the slight differences in completion rates between E1-NEW vs E1-OLD, E2-NEW vs E2-OLD and E3-NEW vs E3-OLD are likely due to random chance.
